---
title: "Read_data_as_Seurat"
author: "Testimony_J_Olumade"
date: "2022-12-16"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install required packages}
# install.packages('Seurat')
library(Seurat)

# SeuratDisk is not currently available on CRAN. You can install it from GitHub with
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github("mojaveazure/seurat-disk")

library(SeuratDisk)
```

## Input formats for sc_RNASeq output data
sc_RNASeq output data can be stored in different formats
1. 10x hdf5 -  stored as .hdf5
2. R data format - stored as .rds
3. Anndata object - stored as .h5ad 
4. Loom - stored as .loom 
5. Text based Market Exchange format - stored as .mtx
6. Tab separated value format - stored as .tsv

## Reading a .RDS document
```{r reading .rds}

rds_object <- readRDS('filename.rds')

# this converts the .rds document into a seurat object
# to view the seurat object

str(rds_object)
```


## Reading a .HDF5 document
```{r reading .hdf5}

hdf5_obj <- read10x_h5(filename = filename.hdf5,
                       use.names = TRUE,
                       unique.features = TRUE)

# this imports the file into the R environment as a dg (dynamic graph) object
# to view the first 10 rows adn columns of the dg object

hdf5_obj [1:10, 1:10]

# to convert the dg object into a seurat object 

seurat_obj <- CreateSeuratObject(counts = hdf5_obj)

# to view the seurat object

str(seurat_obj)
```


## Reading a .MTX document
```{r reading .mtx}

mtx_obj <- ReadMtx(mtx = filename.mtx.gz,
                   features = featuresfile.tsv.gz,
                   cells = barcodefile.tsv.gz)

# this imports the file into the R environment as a dg (dynamic graph) object
# to view the first 10 rows adn columns of the dg object

mtx_obj [1:10, 1:10]

# to convert the dg object into a seurat object 

seurat_mtx <- CreateSeuratObject(counts = mtx_obj)
```


## Reading a .LOOM document
```{r reading .loom}

loom_obj <- connect(filename = filename.loom,
                   mode = 'r')

# this imports the file into the R environment as a dg (dynamic graph) object
# to convert the dg object into a seurat object 

seurat_loom <- as.Seurat(loom_obj)

# to view the seurat object 

str(seurat_loom)
```


## Reading a .H5AD document
```{r reading .h5ad}

# step 1: convert AnnData object to a h5seurat file

convert("filename.h5ad",
        dest = "h5seurat",
        overwrite = TRUE)

# the code above is not assigned to any name
# this is because the 'overwrite' part of the code tells R to simply convert 
# the same document from a .h5ad file to a .h5seurat file

# step 2: load the .h5seurat file into a seurat object 

seurat_anndata <- LoadH5Seurat("filename.h5seurat")

# to view the seurat object 

str(seurat_anndata)
```


## Read a .TSV document
```{r reading tsv}

# convert count data in .tsv format into a data frame object

count.df <- read.delim("countfile.tsv",
                       header = TRUE)

# create a seurat object from the counts data frame object

seurat_tsv <- CreateSeuratObject(counts = count.df)
```

Further analysis on sc_RNASeq data can then be done using seurat in R


